Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-05-05 article.tex
Investigate the tools better

We can predict epitopes.
For MHC-I, \verb;epitope-prediction; is used \richel{Cite Johannes}.
For MHC-II, NetMHCIIpan uses all haplotypes \richel{Cite Morten}.
Although \cite{zhang2015accurate} looks like an even better
method for MHC-II, they only take one haplotype into account.

>>>>

We can predict epitopes.
For MHC-I, \verb;epitope-prediction; is used \richel{Cite Johannes}.

Alternatives are NetMHCcons \cite{karosiene2012netmhccons}.

For MHC-II, NetMHCIIpan (\cite{nielsen2008quantitative,karosiene2013netmhciipan})
uses all haplotypes.
Also \cite{zhang2013predicting} predicts immunogenic T-cell epitopes.
Also \cite{trolle2014nettepi} predicts immunogenic T-cell epitopes.

Although \cite{zhang2015accurate} looks like an even better
method for MHC-II, they only take one haplotype into account.

According to \cite{lundegaard2011prediction}, in 2011, 
NetMHCcons and NetMHCIIpan were the best.
